### 2023-01-19 output/DiD/tables/balance_table.tex
Dropped months w low sample size

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 10,030.65 & 0.18 \\
 & Change, Jan. 2017 to Jan. 2019 & 50,491.60 & 2,664.69 & 0.27 & -23.86 & 0.99 \\
\cline{1-7}
\multirow[c]{6}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.25 & 0.01 & 0.07 & 0.01 & 0.40 \\
 & Jobs per square mile (2010) & 4,158.02 & 263.90 & 0.63 & 122.36 & 0.83 \\
 & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,159.98 & 0.25 \\
 & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 488.36 & 0.17 \\
 & Share white (2010) & 0.60 & 0.04 & 0.00 & 0.02 & 0.06 \\
 & Share with commute $<$15 minutes (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
\cline{1-7}
\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & 0.00 & 0.83 \\
\cline{1-7}
\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.66 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,566.34 & 0.00 & 14,752.11 & 0.14 \\
 & Change, Jan. 2017 to Jan. 2019 & 50,491.60 & 2,654.65 & 0.27 & -2,202.60 & 0.49 \\
\cline{1-7}
\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.25 & 0.01 & 0.07 & 0.00 & 0.96 \\
 & Jobs per square mile (2010) & 4,158.02 & 263.90 & 0.63 & 322.24 & 0.64 \\
 & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,497.45 & 0.24 \\
 & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 787.73 & 0.09 \\
 & Median two bedroom rent (2015) & 1,093.36 & 34.26 & 0.05 & 6.43 & 0.77 \\
 & Share white (2010) & 0.60 & 0.04 & 0.00 & 0.03 & 0.02 \\
 & Share with commute $<$15 minutes (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.60 \\
\cline{1-7}
\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & -0.00 & 0.86 \\
\cline{1-7}
\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.89 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-01-19 output/DiD/tables/pre_treatment_covariate_tests.tex
Dropped months w low sample size

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Zestimate, Dec. 2022 & Plaintiff victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 0.00 & 0.00 \\
 & Change, Jan. 2017 to Jan. 2019 & 0.00 & 0.27 \\
\cline{1-4}
\multirow[c]{7}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.07 \\
 & Jobs per square mile (2010) & 0.00 & 0.63 \\
 & Median household income (2016) & 0.00 & 0.01 \\
 & Share below poverty line & 0.70 & 0.01 \\
 & Population density (2010) & 0.00 & 0.01 \\
 & Share white (2010) & 0.00 & 0.00 \\
 & Share with commute $<$15 minutes (2010) & 0.00 & 0.02 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.01 & 0.68 \\
 & No cause & 0.98 & 0.03 \\
 & Non-payment of rent & 0.31 & 0.77 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.37 & 0.00 \\
 & Plaintiff has an attorney & 0.61 & 0.47 \\
 & Defendant is an entity & 0.02 & 0.37 \\
 & Plaintiff is an entity & 0.62 & 0.13 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Zestimate, Dec. 2022 & Plaintiff victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 0.00 & 0.00 \\
 & Change, Jan. 2017 to Jan. 2019 & 0.00 & 0.27 \\
\cline{1-4}
\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.07 \\
 & Jobs per square mile (2010) & 0.00 & 0.63 \\
 & Median household income (2016) & 0.00 & 0.01 \\
 & Share below poverty line & 0.70 & 0.01 \\
 & Population density (2010) & 0.00 & 0.01 \\
 & Median two bedroom rent (2015) & 0.00 & 0.05 \\
 & Share white (2010) & 0.00 & 0.00 \\
 & Share with commute $<$15 minutes (2010) & 0.00 & 0.02 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.01 & 0.68 \\
 & No cause & 0.98 & 0.03 \\
 & Non-payment of rent & 0.31 & 0.77 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.37 & 0.00 \\
 & Plaintiff has an attorney & 0.61 & 0.47 \\
 & Defendant is an entity & 0.02 & 0.37 \\
 & Plaintiff is an entity & 0.62 & 0.13 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-01-19 output/summary_statistics/tables/summary_statistics.tex
Dropped months w low sample size

\begin{tabular}{llcccc}
\toprule
 &  & Mean & Median & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change, Jan. 2017 to Jan. 2019 & 46,593.74 & 37,330.00 & 158,125.14 & 10,160 \\
 & Zestimate, Jan. 2017 & 298,908.73 & 235,117.00 & 352,754.39 & 10,176 \\
\cline{1-6}
\multirow[c]{7}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,797.07 & 1,355.40 & 17,579.99 & 40,726 \\
 & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
 & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
 & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,726 \\
 & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
 & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,726 \\
 & Share with commute $<$15 minutes (2010) & 0.28 & 0.27 & 0.11 & 40,726 \\
\cline{1-6}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
 & No cause & 0.11 & 0.00 & 0.31 & 40,727 \\
 & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,727 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
 & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,727 \\
 & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,727 \\
\cline{1-6}
\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
 & Case dismised & 0.29 & 0.00 & 0.45 & 40,727 \\
 & Case duration & 57.81 & 21.00 & 78.29 & 39,087 \\
 & Case heard & 0.06 & 0.00 & 0.23 & 40,727 \\
 & Case mediated & 0.41 & 0.00 & 0.49 & 40,727 \\
 & Money judgment & 1,890.34 & 0.00 & 5,279.49 & 40,727 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
 & One year after filing date & 421,601.75 & 347,550.00 & 344,328.86 & 10,443 \\
 & Three years after filing date & 501,611.80 & 414,600.00 & 780,467.01 & 5,894 \\
 & Two years after filing date & 477,948.08 & 393,900.00 & 457,694.83 & 9,175 \\
\cline{1-6}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & Mean & Median & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change, Jan. 2017 to Jan. 2019 & 46,593.74 & 37,330.00 & 158,125.14 & 10,160 \\
 & Zestimate, Jan. 2017 & 298,908.73 & 235,117.00 & 352,754.39 & 10,176 \\
\cline{1-6}
\multirow[c]{8}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,797.07 & 1,355.40 & 17,579.99 & 40,726 \\
 & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
 & Median two bedroom rent (2015) & 1,116.27 & 1,055.00 & 396.29 & 30,537 \\
 & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
 & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,726 \\
 & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
 & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,726 \\
 & Share with commute $<$15 minutes (2010) & 0.28 & 0.27 & 0.11 & 40,726 \\
\cline{1-6}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
 & No cause & 0.11 & 0.00 & 0.31 & 40,727 \\
 & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,727 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
 & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,727 \\
 & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,727 \\
\cline{1-6}
\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
 & Case dismised & 0.29 & 0.00 & 0.45 & 40,727 \\
 & Case duration & 57.81 & 21.00 & 78.29 & 39,087 \\
 & Case heard & 0.06 & 0.00 & 0.23 & 40,727 \\
 & Case mediated & 0.41 & 0.00 & 0.49 & 40,727 \\
 & Money judgment & 1,890.34 & 0.00 & 5,279.49 & 40,727 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
 & One year after filing date & 421,601.75 & 347,550.00 & 344,328.86 & 10,443 \\
 & Three years after filing date & 501,611.80 & 414,600.00 & 780,467.01 & 5,894 \\
 & Two years after filing date & 477,948.08 & 393,900.00 & 457,694.83 & 9,175 \\
\cline{1-6}
\bottomrule
\end{tabular}
